### 2017-02-27 readme.Rmd
update readme

There are two main functions in the `qrbp` package, the first and main function can be used to generate background points within a spatial domain. Generation of background points can be used in Poisson point process modelling in R. The main function is \code{generate_background_points}, which takes a Raster* as a study area, covariates - which are a Raster stack on the of the same resolution and extent as the study area. It is essentially a wrapper around the (excellent and existing) \code{\link[MBHdesign]{quasiSamp}} function in the MBHdesign package which already implements quasi-random sampling within a basic domain.

@@

For a laugh, let's generate some quasirandom background points and plot them against the presence points
```{r}
library(qrbp)
POdata <- species[species$Occurrence == 1,]
bkpts_quasi <- generate_background_points(number_of_background_points = 10000,
                                    known_sites = POdata@coords,
                                    study_area = preds[[1]],
                                    model_covariates = preds,
                                    resolution = 2000,
                                    method = 'quasirandom_covariates')
```

@@

>>>>

There are two main functions in the `qrbp` package, the first and main function can be used to generate background points within a spatial domain. Generation of background points can be used in Poisson point process modelling in R. The main function is `generate_background_points`, which takes a Raster* as a study area, covariates - which are a Raster stack on the of the same resolution and extent as the study area.

@@

For a laugh, let's generate some quasirandom background points and plot them against the presence points. Here we are using the `quasirandom_covariates` method which tries to select quasirandom points across geographic and environmental space. The other working methods are `quasirandom` which just creates quasirandom points spatially, or `grid` which creates a regular grid at a set resolution - this is every similar to the grid design proposed by Warton *et al.,* 2010.
```{r}
library(qrbp)
POdata <- species[species$Occurrence == 1,]
bkpts_quasi <- generate_background_points(number_of_background_points = 10000,
                                    known_sites = POdata@coords,
                                    study_area = preds[[1]],
                                    model_covariates = preds,
                                    resolution = 2000,
                                    method = 'quasirandom_covariates')
```

@@

Warton, D. I., and L. C. Shepherd. "Poisson point process models solve the ???pseudo-absence problem??? for presence-only data in ecology." The Annals of Applied Statistics 4.3 (2010): 1383-1402.
